Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging

### 2015-08-05 writeup/gz_hubble_data.tex
Small changes

%-----------------------------------------------------------------------------------------------------------------------------------
\begin{figure}
\begin{center}
\includegraphics[width=60mm]{example_ferengi2.ps}
%\includegraphics[height=80mm,angle=-90]{TuningFork.ps}
\caption{Examples of an obvious spiral and obvious elliptical at $z=0$ which both look similar when redshifted to $z=0.8$. See below for the description of the method for redshifting.\label{exampleFERENGI}}
\end{center}
\end{figure}
 %-----------------------------------------------------------------------------------------------------------------------------------

@@

\begin{figure*}
\includegraphics[width=160mm]{example_ferengi.ps}
%\includegraphics[height=80mm,angle=-90]{TuningFork.ps}
\caption{Examples of two galaxies which have been run through the \ferengi{} code to produce simulated HST images. The value of $p_{\rm features}$ for each panel is (1) Top row: $p_{\rm features}=$ 0.9, 0.625, 0.35, 0.35, 0.225 and (2) Bottom row: $p_{\rm features}=$ 1.00, 0.875, 0.875, 0.625, 0.375. \label{exampleFERENGI}}
\end{figure*}

@@

The approach used in GZH for correcting the weighted classifications for user bias rests on the assumption that the \emph{amount} of bias is a function of the apparent size and brightness of the image as seen on screen. This is controlled by two types of parameters: \textbf{intrinsic} properties of the galaxy itself, such as its physical diameter and luminosity, and \textbf{extrinsic} properties, such as the distance (redshift) of the galaxy and its relative orientation. There are likely other parameters that affect user accuracy, such as the proximity of close companions \citep[``distraction bias''; see][]{joh15} or those that vary by individual user. The combination of all such parameters forms a high-dimensional space, and we have insufficient test galaxies to measure the individual effects of each. Instead, we use just two parameters that are intended to capture the bulk of the change in bias (based on GZ1/GZ2): one

@@

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{p_vs_p_SB_redshift.ps}
\caption{a caption. Add scale in $p_{\rm features}$ somehow that doesn't clutter the plot even more. }
\label{fig:p_vs_p}
\end{center}
\end{figure*}

>>>>

%-----------------------------------------------------------------------------------------------------------------------------------
\begin{figure}
\begin{center}
\includegraphics[width=60mm]{example_ferengi2.pdf}
%\includegraphics[height=80mm,angle=-90]{TuningFork.pdf}
\caption{Examples of an obvious spiral and obvious elliptical at $z=0$ which both look similar when redshifted to $z=0.8$. See below for the description of the method for redshifting.\label{exampleFERENGI}}
\end{center}
\end{figure}
 %-----------------------------------------------------------------------------------------------------------------------------------

@@

\begin{figure*}
\includegraphics[width=160mm]{example_ferengi.pdf}
%\includegraphics[height=80mm]{TuningFork.pdf}
\caption{Examples of two galaxies which have been run through the FERENGI code to produce simulated HST images. The value of $p_{\rm features}$ for each panel is (1) Top row: $p_{\rm features}=$ 0.9, 0.625, 0.35, 0.35, 0.225 and (2) Bottom row: $p_{\rm features}=$ 1.00, 0.875, 0.875, 0.625, 0.375. \label{exampleFERENGI}}
\end{figure*}

@@

The approach used in GZH for correcting the weighted classifications for user bias rests on the assumption that the \emph{amount} of bias is a function of the apparent size and brightness of the image as seen on screen. This is controlled by two types of parameters: \textbf{intrinsic} properties of the galaxy itself, such as its physical diameter and luminosity, and \textbf{extrinsic} properties, such as the distance (redshift) of the galaxy and its relative orientation. There are likely other parameters that affect user accuracy, such as the proximity of close companions \citep[``distraction bias''; see][]{joh15} or those that vary by individual user. The combination of all such parameters forms a high-dimensional space, and we have insufficient test galaxies to measure the individual effects of each. Instead, we use just two parameters that are intended to capture the bulk of the change in bias (based on GZ1/GZ2): surface brightness (intrinsic) and redshift (extrinsic).

@@

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{p_vs_p_SB_redshift.pdf}
\caption{a caption. Add scale in $p_{\rm features}$ somehow that doesn't clutter the plot even more. }
\label{fig:p_vs_p}
\end{center}
\end{figure*}
